Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-10-08 paper.tex
ref response 2: add error estimate equation

We integrate Eqns.~\ref{eqn:num_x}--\ref{eqn:num_fse} with adaptive step sizes,
using the 3rd order Runge-Kutta algorithm
which produces an error estimate by comparing the 3rd and 2nd order solutions.
After each step is taken, the errors for each of the nine variables of
Eqns.~\ref{eqn:num_x}--\ref{eqn:num_fse} are compared to an absolute and
a relative threshold.
If the error in any variable exceeds its threshold
the step size is decreased and the step recomputed;
if all errors are below threshold, the next step size is increased.
% see OdeIntegrators::AdaptiveDense
% and OdeSteppers::RungeKutta3
% and OdeSteppers::DormandPrince5
% and OdeController
% and OdeControllers::ProportionalIntegral_Base::StepSizeToAttempt
% and OdeErrorMeasures::ScaledAbsRel
% For example, the parameters I use in the nsns data:
%OdeErrorMeasure = ScaledAbsRel
%     (
%      ATol = 0.000555555555555556;
%      RTol = 0.000555555555555556;
%      ScaledVars = q,p,s0,sn,tau,fa,fs;
%      Scales = 4,1,4,4,1e-20,1e-20,1e-20;
In practice, the controlling errors come from the radiation variables
$\tau$, $f_{\rm AE}$, and $f_{\rm SE}$,
for which the relative tolerances are set to $6\times10^{-4}$,
and the absolute tolerances are set to $6\times10^{-24}$.

>>>>

We integrate Eqns.~\ref{eqn:num_x}--\ref{eqn:num_fse} with adaptive step sizes,
using the 3rd order Runge-Kutta algorithm,
from which we compute an error estimate by comparing the 3rd and 2nd order solutions.
After each step is taken, the error estimates $\Delta_i$ for each of the
nine variables of Eqns.~\ref{eqn:num_x}--\ref{eqn:num_fse} are used
to compute an overall error measure of the step, $D$, given by
\begin{equation}
  \label{eqn:err_measure}
  D = \max\left(\frac{\Delta_i}{A+R|V_i|}\right),
\end{equation}
where the max is taken over the set of all variables $V_i$
and their error estimates $\Delta_i$,
and $A$ and $R$ are the absolute and relative error tolerances.
If $D \geq 1$ the step size is decreased and the step recomputed;
if $D < 1$ the next step size is increased.
% The whole integration is run by OdeIntegrator::AdaptiveDense, which contains
%   some essential pieces: 1) OdeStepper calculates the change in the variables,
%   2) OdeErrorMeasure calculates a single double representing the overall error
%   of the step, and 3) OdeController either initiating a step redo or
%   calculating the next step size.
% See:
% * OdeIntegrators::AdaptiveDense
% * OdeErrorMeasures::ScaledAbsRel
% * OdeSteppers::RungeKutta3 and OdeSteppers::DormandPrince5
% * OdeControllers::ProportionalIntegral_Base::StepSizeToAttempt
% For example, the parameters I use in the nsns data:
% ```
% OdeErrorMeasure = ScaledAbsRel(
%   ATol = 0.000555555555555556;
%   RTol = 0.000555555555555556;
%   ScaledVars = q,p,s0,sn,tau,fa,fs;
%   Scales = 4,1,4,4,1e-20,1e-20,1e-20;)
%```
In practice, the controlling errors come from the radiation variables
$\tau$, $f_{\rm AE}$, and $f_{\rm SE}$,
for which the relative tolerances are set to $R=6\times10^{-4}$,
and the absolute tolerances are set to $A=6\times10^{-24}$.
